---
title: "Habitat_Sampler_Usage"
author: "Carsten Neumann"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Habitat_Sampler_Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Workflow of Habitat Sampling and Probability Mapping
```{r setup}
library(HaSa)
```

```R
multi_Class_Sampling(...)
```
## step 1

**A)** an interactive map is plotted in a web browser (firefox for linux), containing:  
a) background map  
b) RGB image  
c) selected habitat type map  
d) probaility threshold on mouse hover  
e) predictive distance  

**B)** the user has to decide to extract this habitat type on the basis of a threshold **(B.1)** or to sample again **(B.2)**

### B.1
```
enter threshold in R console
```
6 files are saved to disk for the selected habitat type  
a) HabitatSampler object (Run) - R Binary  
b) probability map - *.kml, *.png, geocoded *.tif  
c) threshold list - R Binary  
d) leaflet interactive web interface - *.html  
           
after habitat extraction is done the user have to decide to adjust starting number of samples and number of models or proceed automaticlay to the next step
```
enter sample/model adjsutement (../..) or auto (0) in R console
```
## step 2 ... proceed with A)

### B.2
```
enter 0 in R console
```
the user have to decide to adjust starting number of samples and number of models or proceed automaticlay to new sampling
```
enter sample/model adjsutement (../..) or auto (0) in R console
``` 
...proceed with A until decision (B.1) has made

## step 2 ... proceed with A)

--------
### if convergence fails / no models can be selected / init.samples are to little / or another error occurs, restart next step with:
```R
multi_Class_Sampling(in.raster = out.raster, reference = out.reference, classNames = out.names, ... )
```
step = specify next step number

--------
## remarks
1) the results from previous steps are reproducable when using the same seed value and int.seed=Run@seeds (e.g. Run02@seeds) in consequence, init.sample for regular sampling determines an invariant sample distribution, use random sampling or vary init.sample to get varying sample distributions  
2) regular sampling is faster  
3) last = T can be set when only one class should be separated from the background pixels  
4) The R object Run holds slots of:   
models         = selected classifiers  
ref_samples = spatial points of selected samples (see ?write_Out_Samples.r)  
switch          = the target class is [2] if switch is not NA then the target class must be changed from [1] to [2] (see write_Out_Samples.r)  
layer            = raster layer of habitat type probability  
mod_all        = all classifiers from nb_models  
class_ind      = predictive distance metric for all classes  
seeds           = seeds to reproduce respecitve step/habitat type sampling  
5) if multiTest > 1 the user will get multiple maps and will be ask to enter the number of the probability distribution that is apropriate   

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


